\input{../preamble.tex}
\usepackage{todonotes}
\begin{document}

\begin{center}
	\textbf{\large MATH 454: Final Exam Practise} \\
    \\ \large McGill University (Fall 2023)
    \\ Jake R. Gameroff 
\end{center}
Let \( A \subseteq \mathbb{R}^{d}  \) be measurable.
\begin{enumerate}
	\item Let \( f : A \to [0, \infty] \) be integrable. Then for every \( \varepsilon > 0  \) there exists a \( \delta > 0  \) such that for every measurable subset \( E \subseteq A \) with \( m(E) < \delta, \) \( \int_{E} f < \varepsilon  \).
	\item Let \( E \subseteq \mathbb{R}^{d}  \). Show that \( m_*(E) = \inf \{ m(\mathcal{O} ) :E \subseteq  \mathcal{O}, \mathcal{O} \mbox{ open}  \}  \). Use this result to show that \( m_*(E) = \sup_{}\{ m(F) : F \subseteq E, F \mbox{ closed} \}   \).
	\item Let \( f : A \to [0,\infty] \) be measurable. Let \( \{ E_{k}  \} _{ k \in \mathbb{N} }  \) be a sequence of mutually disjoint measurable subsets of \( A \) whose union is \( E \). Show that \[\int_{E} f = \sum_{k \in \mathbb{N} }^{}\int_{E_{k} } f.\]
	\item Let \( \{ f_{k}  \} _{k \in \mathbb{N} }  \) be a sequence of non-negative, measurable functions on \( A \). Show that \(\sum_{k \in \mathbb{N} }^{}f_{k} \) is measurable and \[\int_{A} \sum_{k \in \mathbb{N} }^{}f_{k} = \sum_{k \in \mathbb{N} }^{}\int_{A} f_{k}. \] 
	\item Show that the conclusion of Egorov's theorem can fail if the domain of \( f \) has infinite measure.
	\item Provide a counter-example for each of the following:
		\begin{enumerate}
			\item Show that the bounded convergence theorem does not hold for the Reimann integral.
			\item Show that the bounded convergence theorem does not hold if \( \{ f_{k}  \} _{k \in \mathbb{N} }  \) is a sequence of functions such that for each \( k \in \mathbb{N}  \) there exists an \( m_{k} \in \mathbb{N}   \) such that \( |f_{k} | \leq m_{k}  \) (there is not one \( m \) for every \( k \)).
			\item Show that \( \leq \) can be strict in Fatou's lemma
			\item Let \( E = E_1 \times E_2 \subseteq \mathbb{R}^{d_1} \times \mathbb{R}^{d_2}   \) be measurable. Are \( E_1 \) and \( E_2 \) measurable?
		\end{enumerate}
	\item State and prove Chebyshev's inequality. Show that \( \int_{A} f = 0 \iff f= 0  \) a.e. in \( A \). Show that \( \int_{A} f < \infty\implies  \) \( f < \infty \) a.e. in \( A \).
	\item Let \( f : A \to \mathbb{R} \) be bounded and measurable. Show that there exists a sequence of simple functions that converge uniformly to \( f \) in \( A \).
	\item Let \( A \subseteq \mathbb{R}^{d - 1}  \) be measurable and \( f : A \to [0, \infty ]\) be a function. Show that \( f \) is measurable if and only if \[\Gamma \coloneqq \{ (x,y) \in \mathbb{R}^{d- 1} \times \mathbb{R} : 0 \leq y \leq f(x) \} \] is measurable. Also, if \( f \) is measurable, show that \( m(E) = \int_{A} f \).
	\item Let \( A \subseteq \mathbb{R}^{d}  \) be measurable. Show that for almost every \( y \in \mathbb{R}^{d_2}  \), (a) \( A^{y}  \) is measurable, (b) \( y \mapsto m(A^{y})  \) is measurable, and (c) \( \int_{\mathbb{R}^{d_2} }  m(A^{y} ) = m(A)\).
	\item State the definition of Lipschitz continuity. Show that if \( f : [a,b] \to \mathbb{R} \) is continuous and differentiable in \( (a,b) \), and \( f' \) is bounded, then \( f \) is of bounded variation on \( [a,b] \).
	\item Show that \( f : [a,b] \to \mathbb{R} \) is of bounded variation if and only if it can be written as the difference of two increasing functions.
	\item State both the simple approximation lemma and simple approximation theorem. Show that the simple approximation gives a sequence of simple functions that converge \emph{uniformly} to \( f \) on its domain.
	
	
	
	
	
\end{enumerate}
\end{document}
